Lambda Calculus through Tropical Mathematics

### 2023-01-12 section6.tex
commit

Notice that, when $f:!(\Lawv^{X})\to \Lawv^{Y}$, so that $f$ is described by a matrix $\widehat f: \multiset(X)\times Y\to \Lawv$, one can check that \eqref{eq:dermod} coincides with the definition of the differential operator in $\LREL$.

>>>>

Notice that, when $f:!(\Lawv^{X})\to \Lawv^{Y}$, so that $f$ is described by a matrix $\widehat f: \multiset(X)\times Y\to \Lawv$, one can check that the matrix associated with \eqref{eq:dermod} coincides with the definition of the differential operator in $\LREL$.
